Reading Notes

### 2020-02-14 paper.tex
quick habit

other notes:
CG methods--IBI, force matching, inverse MC. This paper goes over details of these and how they're implemented in votca. This wasn't really what I wanted to read about so I skimmed.
They use ESPResSo++ for quantum calculations
OK, this isn't the right paper to read about CT stuff or backmapping. Let's look at some of these [http://www.votca.org/citations/using-votca](http://www.votca.org/citations/using-votca)
Also I'm noticing in this list of papers--Marrink (cited by chakraborty) is here and there is a paper mentioning the importance of side-chains for charge-mobility! \cite{May2011}
Next time read about tie-chains \cite{May2011} and/or charge mobility \cite{Lukyanov2010}
\bibliography{library}
\bibliographystyle{ieeetr}
\end{document}

>>>>

other notes:
CG methods--IBI, force matching, inverse MC. This paper goes over details of these and how they're implemented in votca. This wasn't really what I wanted to read about so I skimmed.
They use ESPResSo++ for quantum calculations
OK, this isn't the right paper to read about CT stuff or backmapping. Let's look at some of these [http://www.votca.org/citations/using-votca](http://www.votca.org/citations/using-votca)
Also I'm noticing in this list of papers--Marrink (cited by chakraborty) is here and there is a paper mentioning the importance of side-chains for charge-mobility! \cite{May2011}
Next time read about tie-chains \cite{May2011} and/or charge mobility \cite{Lukyanov2010}
Lukyanov--sounds a lot like morphct, gaussian density of states? I thought their (votca's) method was like morphct but now I'm not sure... It seems like they're using a simplification and not doing dft.
\bibliography{library}
\bibliographystyle{ieeetr}
\end{document}
